DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/exp_setup.tex
abstract and introduction review

\subsection{Evaluation}
The evaluation of our proposed method is conducted through running inference on both seen and unseen data of different lengths. These results of the network are compared to the output of HEFT and GA methods in the same scenarios.

>>>>

\subsection{Evaluation}
Fig.\ref{fig:efw} shows our evaluation framework of the network. The evaluation of our proposed method is conducted through running inference on both seen and unseen data of different lengths. These results of the network are compared to the output of HEFT and GA methods in the same scenarios.

### 2020-04-12 paper/core/introduction.tex
added experimental setup section
abstract and introduction review

\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) have driven our needs for better resource allocation methods. 
The performance of any system critically depends on the algorithms used to schedule tasks on its resources. These systems contain limited resources, that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion. 
The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\

@@

However, this comes with the problem of complex task scheduling. The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem. \\

The parameters of such problem make it very suitable for various optimization techniques. Recursive optimization techniques are very efficient in solving many optimization problem. Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem. Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated. \\

In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem. This learned representation will be used to approximate the scheduling performance of other scheduling techniques. \emph{Neural Networks} are our best candidate for this task. Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others. They have proven to be more efficient than other traditional methods. The complexity of the neural networks comes in the development phases, where the network is designed and trained. However, in inference phase, neural networks can achieve very accurate results at high speed. Recent work has been done on optimizing neural network inference through various techniques, such as quantization \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}. \\

The recent advances in \emph{Deep Learning} research is considered in designing and training our scheduling network. \emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance. Also, we include a genetic algorithm experiment for the same problem for comparison. We will discuss our approach to the problem and its limitations.

>>>>

\IEEEPARstart{T}{he} continuous evolution of computing power and growth of widely-distributed applications and \emph{Internet of Things} (IoT) \cite{inproceedings} have driven our needs for better resource allocation methods. 
The performance of any system critically depends on the algorithms used to schedule tasks on its resources. These systems contain limited resources that should be allocated properly, in order to perform the required tasks with maximum efficiency avoiding starvation and resource exhaustion. 
The general objective of any scheduling technique is to get the best possible performance with a reasonable resource utilization. \\

@@

However, this comes with the problem of complex task scheduling process. The task scheduling problem for a heterogeneous computing system is more complex than that for a homogeneous system, because of the different execution rates of processors and different communication rates among different processors, which add extra layers of complexity to the problem. \\

The first type of methods to turn to is greedy-based methods, where the best possible choice in the current situation is considered. The execution time of these methods rapidly increases with input size and their performance degrades in complex situations. However, the parameters of the scheduling problem in heterogeneous distributed systems make it very suitable for various optimization techniques. Recursive optimization techniques are very efficient in solving many optimization problem. Previous work has investigated the usage of techniques such as \emph{genetic algorithms} \cite{article2} to solve the task scheduling problem. Also, the usage of a progressive decision making techniques such as \emph{Reinforcement Learning} \cite{ORHEAN2018292} for task scheduling in heterogeneous systems has been investigated. \\

In this paper, we investigate the ability of advanced predictive models to learn a representation of static local task scheduling problem. This learned representation is used to approximate the scheduling performance of other scheduling techniques. \emph{Neural Networks} are our best candidate for this task. Neural networks are being used in many fields replacing traditional methods, such as image classification \cite{10.1145/3065386}, object detection \cite{ren2015faster}, neural language modelling \cite{ren2015faster}, image generation \cite{karras2019analyzing} and others. They have proven to be more efficient than other traditional methods. The complexity of the neural networks comes in the development phases, where the network is designed and trained. However, in inference phase, neural networks can achieve very accurate results at high speed. Recent work has been done on optimizing neural network inference through various techniques, such as quantization \cite{choukroun2019lowbit} and pruning \cite{yeom2019pruning}. \\

The recent advances in \emph{Deep Learning} research are considered in designing and training our scheduling network. \emph{Heterogeneous Earliest Time First} (HEFT) \cite{993206} is used as a target, where the network learns to approximate its performance. Also, we include a genetic algorithm experiment for the same problem for comparison. We will discuss our approach to the problem and its limitations.

### 2020-04-12 paper/paper.tex
added future work
abstract and introduction review

\begin{abstract}
Task scheduling is one of the core problems in any distributed system. The ability of the system to assign tasks to its different resources to achieve the best possible performance with the least resource consumption is the main challenge in distributed systems research. The heterogeneity of the distributed systems adds another layer of complexity on top of the mentioned problem. The different execution time on different processors and different task dependencies make the scheduling problem very computationally intensive. Usually, researchers and developers turn to greedy-based methods or even recursive optimization methods to reach some optimal or sub-optimal solution. However, due to the nature of the problem, these solutions might take very long time and usually degrade in complex situations. In this work, we propose the idea of scheduling algorithms approximation, where we approximate the complex scheduling algorithms using other models to achieve the same results but with lower execution time. Neural networks are proposed for this task, as they are great function approximators. The complexity of neural networks comes at training time, however they can maintain constant execution time in inference. This constant execution time is relatively low, as it's a simple feedforward process. This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios, which is useful in some case such as simulation workflow on supercomputers. The proposed network can achieve almost the same performance of the approximated method (HEFT) on seen data during training and slightly worse performance on unseen data.
\end{abstract}

@@

\section{Conclusion}
\input{core/conclusion}

\section{Future Work}
\input{core/future_work}

>>>>

\begin{abstract}
Task scheduling is one of the core problems in any distributed system. The ability of the system to assign tasks to its different resources to achieve the best possible performance with the least resource consumption is the main challenge in distributed systems research. The heterogeneity of the distributed systems adds another layer of complexity on top of the mentioned problem. The different execution time on different processors and different task dependencies make the scheduling problem very computationally intensive. Usually, researchers and developers turn to greedy-based methods or even recursive optimization methods to reach some optimal or sub-optimal solutions. However, due to the nature of the problem, these solutions might take very long time and usually degrade in complex situations. In this work, we propose the idea of scheduling algorithms approximation, where we approximate the complex scheduling algorithms using other models to achieve the same results but with lower execution time. Neural networks are proposed for this task, as they are great function approximators. The complexity of neural networks comes at training time, however they can maintain constant execution time in inference. This constant execution time is relatively low, as it's a simple feedforward process. This makes neural networks a perfect candidate for us, however this comes at a cost of static scheduling scenarios, which is useful in some case such as simulation workflow on supercomputers. The proposed network can achieve almost the same performance of the approximated method (HEFT) on seen data during training and slightly worse performance on unseen data with constant execution time at different input sizes.
\end{abstract}

@@

\section{Conclusion and Future Work}
\input{core/conclusion}
